{\small Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices}

### 2017-11-13 Meetings/GPMNov2017/gpm_november2017_topic21.tex
updated to GpM slides

\begin{frame}{Program for 2018: AUG}
  \begin{itemize}
     \item X-point manipulator (NPH ?) simultaneously with MEM
     \item X-point vertical shift in order to have SP at different
	vertical height at the target. \alert{We will observe similar
          observation as obtained in JET when moving from horizontal
          to vertical target?}
     \item DN discharges. With slow movement of the second X-point into the vessel
	to be performed at constant power/density where shoulder
        alreay exists. \alert{This is mandatory to complement the
          information obtained on TCV}
     \item USN with midplane/X-point manipulator to monitor the upstream SOL 
\end{itemize}
 \end{frame}
 \begin{frame}{MST2-NPH}
   \begin{columns}
     \begin{column}{0.5\textwidth}
       \centering{\includegraphics[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/NPH_2018}}
     \end{column}
     \begin{column}{0.5\textwidth}
       \begin{itemize}
         \item MST2 founded project for the realization of a New Probe
           Head (NPH) (C. Ionita,  B. Schneider \textit{et al})
         \item Simultaneous information on Ion temperature (2 RFAs),
           Plasma potential and electron temperature (Emissive probe
           coupled with floating potential) and magnetic fluctuations
           from 2 3-axial magnetic pick up coil
         \item Potentially tested on TCV beginning of 2018 and then
           moved to other MST1 devices
       \end{itemize}
     \end{column}
   \end{columns}

@@

\begin{frame}{Program for 2018: TCV}
  \begin{itemize}
     \item H-Mode ?
      \item Long divertor legs (probe in the lower port)
      \item SnowFlake to monitor the fluctuations in between the 2 separatrix
	to be done in high density discharges
       \item Try to move the second X-point in SN divertor at a different
	Z position while keeping the same radial distances between the
	points
\end{itemize}
\end{frame}

\begin{frame}{Program for 2018: MAST-U}
  \begin{itemize}
     \item Influence of neutral recycling source in establishing upstream profiles
	and comparison between Low-RT and Vertical target. Look also ath the heat
	loads
      \item Current scan at constant q95/constant Bt
      \end{itemize}
\end{frame}

>>>>

\begin{frame}{Program for 2018: AUG}
  \begin{itemize}
     \item X-point manipulator (NPH ?) simultaneously with MEM
     \item X-point vertical shift in order to have SP at different
	vertical height at the target. \alert{We will observe similar
          observation as obtained in JET when moving from horizontal
          to vertical target?}
     \item DN discharges. With slow movement of the second X-point into the vessel
	to be performed at constant power/density where shoulder
        alreay exists. \alert{This is mandatory to complement the
          information obtained on TCV}
     \item USN with midplane/X-point manipulator to monitor the
       upstream SOL 
\item
\end{itemize}
 \end{frame}
 \begin{frame}{MST2-NPH}
   \begin{columns}
     \begin{column}{0.5\textwidth}
       \centering{\includegraphics[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/NPH_2018}}
     \end{column}
     \begin{column}{0.5\textwidth}
       \begin{itemize}
         \item MST2 founded project for the realization of a New Probe
           Head (NPH) (C. Ionita,  B. Schneider \textit{et al})
         \item Simultaneous information on Ion temperature (2 RFAs),
           Plasma potential and electron temperature (Emissive probe
           coupled with floating potential) and magnetic fluctuations
           from 2 3-axial magnetic pick up coil
         \item Potentially tested on TCV beginning of 2018 and then
           moved to other MST1 devices
         \item Heat load
       \end{itemize}
     \end{column}
   \end{columns}

@@

\begin{frame}{Program for 2018: TCV}
  \begin{itemize}
     \item \textcolor{consorziored}{H-Mode} 
      \item Long divertor legs (probe in the lower port) to check if
        increase of filamentary transport along the divertor leg
        exists in high density scenarios
      \item \textcolor{taorange}{SnowFlake to monitor the fluctuations in between the 2 separatrix
	to be done in high density discharges}
       \item \textcolor{taorange}{Try to move the second X-point in SN divertor at a different
	Z position while keeping the same radial distances between the
	points}
\end{itemize}
\end{frame}

\begin{frame}{Program for 2018: MAST-U}
  \begin{itemize}
      \item Current scan at constant q95/constant Bt
      \item Influence of neutral recycling source in establishing upstream profiles
	and comparison between Low-RT and Vertical target. Look also a
        the heat loads
      \end{itemize}
\end{frame}
